Initial Biome Composition Analysis

### 2018-06-14 Initial Community Composition.Rmd
John comments June 13

#set working directory
require(knitr)
opts_knit$set(root.dir = "C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data")
setwd("C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data")
getwd()

#load necessary packages -- "library" or "require"
require(tidyverse)
require(data.table)
require(rmarkdown)
require(ggplot2)
require(dplyr)

@@

#Filter for inital reads and organize by phyla
abun_tax <- abun_tax %>%
  filter(Hour == 0) %>%
  group_by(mouseid, Phylum)

@@

tempz <- tempz[order(mouseid, Phylum),]

@@

>>>>

#set working directory
require(knitr)
opts_knit$set(root.dir = "C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data") #I'm not familiar with this approach
setwd("C:/Users/Timothy Brennhofer/Desktop/KBS REU/KBS Data") #not sure but the spaces ('white spaces') may be messing it up. Or, you may want to add a '\' to the end of the directory. But it's fine just to refer to the file directories directly. 
getwd()

#load necessary packages -- "library" or "require"
require(tidyverse) #this includes ggplot and dplyr - no need to load them separately
require(data.table)

@@

#Filter for inital reads and organize by phyla
#why alter abun_tax permanently?
abun_tax <- abun_tax %>%
  filter(Hour == 0) %>%
  group_by(mouseid, Phylum)

@@

#Note that this won't do anything; ggplot will plot things alphabetically unless you format the column as a "factor" (google it)
tempz <- tempz[order(mouseid, Phylum),]

@@

#the problem here is that the paste0() function fills the "percentabun"column with "character" values, as opposed to "number" values. Thus, ggplot doesn't know how to plot character-based data in a quantitative way. Why not just:

ggplot(abun_tax, aes(x = mouseid, y = abun, fill = Phylum)) +
  geom_bar(stat = "identity")
